Influences of GDP in the U.S

### 2022-11-12 Manuscript/manuscript.tex
commit

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{AVP1}
\end{figure}

>>>>

"A strong linear relationship in the added variable plot indicates the increased importance of the contribution of X to the model already containing the other predictors.

@@

The Added Variable Plots for the model are as follows:

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{AVP1}
  \caption{This figure shows the AV Plots for the variables included in Model 1}
\end{figure}
